**Supplementary Information**

### 2020-11-21 submission/supplementary.Rmd

## Supplementary Figures

@@

\newpage
## Supplementary Table

@@

# Loading sequence statistics following eggNOG mapper
eggnog_45 <- read_tsv("results/metagenomics/statistics/07eggnog_45.txt", col_names=FALSE)
eggnog_47 <- read_tsv("results/metagenomics/statistics/07eggnog_47.txt", col_names=FALSE)
eggnog_61 <- read_tsv("results/metagenomics/statistics/07eggnog_61.txt", col_names=FALSE)
eggnog_63 <- read_tsv("results/metagenomics/statistics/07eggnog_63.txt", col_names=FALSE)

@@

# Generating the table
kable(metadata_metagenomic_statistics, format="latex", booktabs=TRUE, linesep="", longtable=TRUE, escape=FALSE, col.names=linebreak(c("Sample ID", "Station", "Community Type", "Date", "No. of Raw\nSequence Pairs", "No. of\nContigs", "N50\\textsuperscript{*}", "L50 (bp)\\textsuperscript{*}", "No. of\nPredicted\nCDS", "No. of\nAnnotated\nCDS"), align="c"), caption="Sample ID, sampling station, community type, sampling date, number of raw sequence pairs, number of assembled contigs by MEGAHIT, N50 and L50 assembly statistics, number of predicted coding sequences (CDS) by Prodigal and number of eggNOGmapper annotated CDS.\\label{metagenomic_statistics}", align="c") %>%
  kable_styling(latex_options=c("hold_position", "repeat_header"), font_size=9) %>%
  row_spec(0, bold=TRUE) %>%
  column_spec(1, width="5em") %>%
  footnote(symbol="The notation was preserved from the original output of BBTools stats.sh.")
```

@@

# Generating the table
select(metadata_metagenomic_phylum, phylum, cds, cds_relative, rpkm, rpkm_relative) %>%
kable(format="latex", booktabs=TRUE, linesep="", longtable=TRUE, escape=FALSE, col.names=linebreak(c("Phylum", "No. of CDS", "CDS (\\%)", "Summed RPKM", "RPKM (\\%)"), align="c"), caption="Phyla into which CDS were classifed, number and proportion of CDS in different phyla and sum of coding sequences' RPKM (Reads Per Kilobase Million) and their proportion in different phyla. Data are derived from sequenced metagenomes. Each metagenomic sample is labeled with sampling station, community type, sampling date and sample ID. For each sample top ten phyla based on RPKM were selected. CDS that were not successfully classified were excluded from the dataset.\\label{metagenomic_taxonomy}", align="c") %>%
  kable_styling(latex_options=c("hold_position", "repeat_header"), font_size=9, full_width=TRUE) %>%
  row_spec(0, bold=TRUE) %>%
  group_rows("Funtana, \\\\textit{Cymodocea nodosa} (Mixed), 14 December 2017 (sample ID: 45)", 1, 10, escape=FALSE, latex_gap_space="0.6 em") %>%
  group_rows("Funtana, \\\\textit{Caulerpa cylindracea} (Monospecific), 14 December 2017 (sample ID: 47)", 11, 20, escape=FALSE, latex_gap_space="0.6 em") %>%
  group_rows("Funtana, \\\\textit{Cymodocea nodosa} (Mixed), 19 June 2018 (sample ID: 61)", 21, 30, escape=FALSE, latex_gap_space="0.9 em") %>%
  group_rows("Funtana, \\\\textit{Caulerpa cylindracea} (Monospecific), 19 June 2018 (sample ID: 63)", 31, 40, escape=FALSE, latex_gap_space="0.6 em")
```

>>>>

## Supplementary figure

@@

\newpage
## Supplementary tables

@@

# Loading sequence statistics following eggNOG-mapper
eggnog_45 <- read_tsv("results/metagenomics/statistics/07eggnog_45.txt", col_names=FALSE)
eggnog_47 <- read_tsv("results/metagenomics/statistics/07eggnog_47.txt", col_names=FALSE)
eggnog_61 <- read_tsv("results/metagenomics/statistics/07eggnog_61.txt", col_names=FALSE)
eggnog_63 <- read_tsv("results/metagenomics/statistics/07eggnog_63.txt", col_names=FALSE)

@@

# Generating the table
kable(metadata_metagenomic_statistics, format="latex", booktabs=TRUE, linesep="", longtable=TRUE, escape=FALSE, col.names=linebreak(c("Sample ID", "Station", "Community Type", "Date", "No. of Raw\nSequence Pairs", "No. of\nContigs", "N50\\textsuperscript{*}", "L50 (bp)\\textsuperscript{*}", "No. of\nPredicted\nCDS", "No. of\nAnnotated\nCDS"), align="c"), caption="Sample ID, sampling station, community type, sampling date, number of raw sequence pairs, number of assembled contigs by MEGAHIT, N50 and L50 assembly statistics, number of predicted coding sequences (CDS) by Prodigal and number of eggNOG-mapper annotated CDS.\\label{metagenomic_statistics}", align="c") %>%
  kable_styling(latex_options=c("hold_position", "repeat_header"), font_size=9) %>%
  row_spec(0, bold=TRUE) %>%
  column_spec(1, width="5em") %>%
  footnote(symbol="The notation was preserved from the original output of BBTools stats.sh.")
```

@@

# Generating the table
select(metadata_metagenomic_phylum, phylum, cds, cds_relative, rpkm, rpkm_relative) %>%
kable(format="latex", booktabs=TRUE, linesep="", longtable=TRUE, escape=FALSE, col.names=linebreak(c("Phylum", "No. of CDS", "CDS (\\%)", "Summed RPKM", "RPKM (\\%)"), align="c"), caption="Phyla into which CDS were classified, number and proportion of CDS in different phyla and sum of coding sequences' RPKM (Reads Per Kilobase Million) and their proportion in different phyla. Data are derived from sequenced metagenomes. Each metagenomic sample is labelled with sampling station, community type, sampling date and sample ID. For each sample top ten phyla based on RPKM were selected. CDS that were not successfully classified were excluded from the dataset.\\label{metagenomic_taxonomy}", align="c") %>%
  kable_styling(latex_options=c("hold_position", "repeat_header"), font_size=9, full_width=TRUE) %>%
  row_spec(0, bold=TRUE) %>%
  group_rows("Funtana, \\\\textit{Cymodocea nodosa} (Mixed), 14 December 2017 (sample ID: 45)", 1, 10, escape=FALSE, latex_gap_space="0.6 em") %>%
  group_rows("Funtana, \\\\textit{Caulerpa cylindracea} (Monospecific), 14 December 2017 (sample ID: 47)", 11, 20, escape=FALSE, latex_gap_space="0.6 em") %>%
  group_rows("Funtana, \\\\textit{Cymodocea nodosa} (Mixed), 19 June 2018 (sample ID: 61)", 21, 30, escape=FALSE, latex_gap_space="0.9 em") %>%
  group_rows("Funtana, \\\\textit{Caulerpa cylindracea} (Monospecific), 19 June 2018 (sample ID: 63)", 31, 40, escape=FALSE, latex_gap_space="0.6 em")
```
